% !Mode:: "TeX:UTF-8" 

\defaultfont
\BiAppendixChapter{攻读\cxuewei 学位期间发表的论文及其他成果} {Papers published in the period of PH.D. education}
\setlength{\parindent}{0em}
\textbf{一、发表的学术论文}
\begin{publist}
\item XXX. Online Object Tracking Based on BLSTM-RNN with Contextual-Sequential Labeling[C]. \textcolor{blue}{IEEE Transactions on Multimedia (TMM)} (under review).（\underline{\bf SCI 2区}）
\item XXX. Tennis Ball Tracking Using A Two-layered Data Association Approach[J]. \textcolor{blue}{IEEE Transactions on Multimedia (TMM)}, 2015, 17(2): 145-156.（\underline{\bf SCI 2区}）
\item XXX. Online Object Tracking Based on CNN with Metropolis-Hasting Re-sampling[C]. In \textcolor{blue}{ACM international conference on Multimedia (ACMMM)}, Brisbane, Australia, 2015: 1163-1166.（\underline{\bf CCF A类会议}）
\item XXX. An Ensemble of Deep Neural Networks for Object Tracking[C]. In \textcolor{blue}{IEEE International Conference on Image Processing (ICIP)}, Paris, France, 2014: 843-847.（\underline{\bf CCF C类会议}，获选大会Top10\%文章）
\item XXX. Unsupervised Broadcast News Story Segmentation Using Distance Dependent Chinese Restaurant Processes[C]. \textcolor{blue}{The 39th International Conference on Acoustics, Speech, and Signal Processing (ICASSP)}, Florence, Italy, 2014: 4062-4066.（\underline{\bf CCF B类会议}）
\item XXX. A Two Layered Data Association Approach for Ball Tracking[C]. In \textcolor{blue}{IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP)}, Vancouver, Canada, 2013: 2317-2321.（\underline{\bf CCF B类会议}）
\item XXX. Detection of Ball Hits in A Tennis Game Using Audio and Visual Information[C]. In \textcolor{blue}{IEEE Asia-Pacific Signal Information Processing Association Annual Summit and Conference (APSIPA ASC)}, Hollywood, California, 2012: 1-10.
\item XXX. Real-time Speech-driven Virtual Avatar[J]. \textcolor{blue}{Journal of Tsinghua University}, 2011, 51(9): 1180-1186.（\underline{\bf NCMMSC最佳学生论文提名}）
\item XXX. Speech and Auditory Interfaces for Ubiquitous, Immersive and Personalized Applications[C]. In \textcolor{blue}{Immersive and Personalized Applications, Ubiquitous Intelligence Computing and the 7th International Conference on Autonomic Trusted Computing (UIC/ATC)}, Xi’an, China, 2010: 503-505.
\end{publist}
\vspace{0.5cm}

\textbf{二、博士期间的获奖情况}
\begin{publist}
 \item ICIP 2014 Top\%10 Paper Award.({\bf 第一作者})
 \item 第10届京港国际博士生论坛Best Paper.({\bf 第一作者})
 \item 获2016年XXXX大学计算机学院“图灵之星”奖
 \item 获2015年XXXX大学“理光奖学金”
 \item 获2015年XXXX大学“海泰奖学金”
\end{publist}
% \textbf{二、参与的科研项目及获奖情况}
% \begin{publist}
% \item XX. Towards A Queue-Aware ATM: Monitoring and Managing Queues in Front of ATMs, NCR英国国际合作项目.课题编号：XXXX.
% \item XX. 语音内容分析的关键技术研究, 陕西省自然科学基础研究计划.课题编号：XXXX.
% \item XX. 基于DBN协同建模的中文及跨语种语音结构事件检测研究, 国家自然科学基金.课题编号：XXXX.
% \item XX. 机载语音处理技术,	研究所合作项目.课题编号：XXXX.
% \end{publist}
% \vfill
% \hangafter=1\hangindent=2em\noindent

% \setlength{\parindent}{2em}
\clearpage\mbox{}